
\documentclass[12pt]{spec}

\begin{document}

\specheader
\bigskip
\hrule

\spectitle{Universal Complaint Format Specification}{VERSION: v0.1 | Author: Prathu Baronia}

\section{Overview}

\specjust{A standardized open-source TOML-based format for registering generic
complaints against public or private entities. This format
is \textbf{citizen-facing} and focuses on interoperability across different
complaint systems, departments, and municipalities.}

\specnote{It is \textbf{not} designed for internal workflow or tracking by public departments.}

\input{structure.tex}

\input{section_descriptions.tex}

% TODO: wrap this in a box
\input{example_ucf.tex}

\section{Compliance}

A file is considered UCF-compliant if:

\begin{itemize}
  \item It conforms to TOML v1.0.0.
  \item It includes the mandatory sections and required keys.
  \item Datetime should be RFC 3339 formatted.
  \item Booleans should be lowercase true/false.
  \item Optional sections, if present, respect type and naming rules.
  \item Arrays: Only [[]] are allowed for repeated structures (attachments)
\end{itemize}

\section{FAQs}

\begin{specpara}{Why TOML?}
\href{https://toml.io/en}{TOML} is human-readable, simple, and supported across many
programming \href{https://github.com/toml-lang/toml/wiki}{languages}. Its 
well-defined syntax ensures minimal ambiguity, making UCF files easy to parse, 
validate, and generate.
\end{specpara}

\begin{specpara}{Which fields will be autopopulated?}
Fields like `name`, `contact`, `location`, and `auth-id` from user profiles and
device metadata.
\end{specpara}

\begin{specpara}{How blockchain helps here?}
A hash (e.g., SHA256 of the entire `.ucf` file) can be embedded or stored
separately in on-chain complaint registries for verification.
\end{specpara}

\begin{specpara}{Is it extensible?}
Departments can introduce new optional tables
(e.g., `[complaint-meta]`, `[response-records]`) without breaking
compatibility.
\end{specpara}

\begin{specpara}{Is it interoperable?}
Because TOML is widely supported, implementations in various languages (Python,
Go, Rust, Node.js, etc.) can easily parse or generate `.ucf` files. So
multiple system implementations can work easily with the same format.
\end{specpara}

\begin{specpara}{Is privacy a concern here?}
Sensitive citizen information (e.g., name, contact numbers) would be encrypted.
The plain text citizen info shown above is just for ease of readability.
\end{specpara}

\end{document}
